Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2021-09-13 vertical-thermal-review.Rmd
edit Fig. 3 caption, as per issue #64
#64

![**Figure `r fig_leaf_T`. Theoretical expectations for variation in the difference between leaf and air temperatures, $T_{leaf}-T_{air}$, in response to (a) shortwave radiation, (b) wind speed, (c) relative humidity, (d) leaf width, and (e) stomatal conductance.** Leaf temperatures were modeled using the  *tealeaves* R package of @muir_tealeaves_2019 parameterized to represent typical conditions for a broadleaf species (*Quercus rubra* L.) in a mesic temperate forest (Harvard Forest, Massachusetts, USA) under both normal and drought conditions, as detailed in Supplementary Information Methods `r appendix_tealeaves_methods`. In each scenario, an the independent variable was allowed to vary while other parameters were held constant at the values given in the table of biophysical constants. swr = short wave radiation (W/m^2^); ws = windspeed (m/s); rh= relative humidity; lw = leaf width (cm); gs = stomatal conductance (mmol m^2^/s). ](leaf_energy_balance/fig3_leafenergy.png)

>>>>

![**Figure `r fig_leaf_T`. Theoretical expectations for variation in the difference between leaf and air temperatures, $T_{leaf}-T_{air}$, in response to (a) shortwave radiation, (b) wind speed, (c) relative humidity, (d) leaf width, and (e) stomatal conductance.** Leaf temperatures were modeled using the  *tealeaves* R package of @muir_tealeaves_2019 parameterized to represent a broadleaf species (*Quercus rubra* L.) in a mesic temperate forest (Harvard Forest, Massachusetts, USA) under both humid and drought conditions, as detailed in Supplementary Information Methods `r appendix_tealeaves_methods`. In each scenario, an the independent variable was allowed to vary while other parameters were held constant at the values given in the table of biophysical constants. swr = short wave radiation (W/m^2^); ws = windspeed (m/s); rh= relative humidity; lw = leaf width (cm); gs = stomatal conductance (mmol m^2^/s). ](leaf_energy_balance/fig3_leafenergy.png)
